Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-18 paper/main.tex
clean up diversity graphs

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=2,
      title=Linkage: \method
    ]
    \addplot table[x=threshold, y=python_twenty_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
\end{axis}
\end{tikzpicture}
}
\caption{The number of clusters when clustering a baseline of twenty dissimilar programs from
  Rosetta Code.}
\label{fig:diversity-baseline}
\end{figure}

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=1000,
      title=Linkage: \method
    ]
    \foreach \language in {ocaml, python}
    {
      \addplot table[x=threshold, y=\language_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
    }
\legend{OCaml, Python}
\end{axis}
\end{tikzpicture}
}
\caption{Number of clusters when data is clustered by single, complete, and average linkage.
  A linkage tree is built using agglomerative clustering, and the resulting tree is broken up
  into clusters by thresholding the inconsistency coefficient. The inconsistency coefficient
  of a link is its distance, z-scored against other nearby links.}
\label{fig:diversity}
\end{figure}

>>>>

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=2,
      title=Linkage: \method
    ]
    \addplot+[mark=none] table[x=threshold, y=python_twenty_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
\end{axis}
\end{tikzpicture}
}
\caption{The number of clusters when clustering a baseline of twenty dissimilar programs from
  Rosetta Code. We give no plot for the baseline of 5000 identical programs, as they were
  consistently placed in just 1 cluster.}
\label{fig:diversity-baseline}
\end{figure}

\begin{figure}
\foreach \method in {single, complete, average}
{
\begin{tikzpicture}
  \begin{axis}[
      xlabel=Threshold,
      ylabel=\# of clusters,
      ytick distance=1000,
      title=Linkage: \method
    ]
    \foreach \language in {ocaml, python}
    {
      \addplot+[mark=none] table[x=threshold, y=\language_cluster_counts_\method, col sep=comma]{cluster_counts.csv};
    }
\legend{OCaml, Python}
\end{axis}
\end{tikzpicture}
}
\caption{Number of clusters when data is clustered by single, complete, and average linkage.
  A linkage tree is built using agglomerative clustering, and the resulting tree is broken up
  into clusters by thresholding the inconsistency coefficient. The inconsistency coefficient
  of a link is its distance, z-scored against other nearby links.}
\label{fig:diversity}
\end{figure}
